---
title: "Across"
---

```{r}
library(tidyverse)
```


## Generate some data
```{r}
set.seed(123)
sales <- tibble(
  prod_id = c(rep("A", 3), rep("B", 3), rep("C", 4)),
  Jan = sample(100:500, 10, replace = TRUE),
  Feb = sample(100:500, 10, replace = TRUE),
  Mar = sample(100:500, 10, replace = TRUE),
  Apr = sample(100:500, 10, replace = TRUE),
  May = sample(100:500, 10, replace = TRUE),
  Jun = sample(100:500, 10, replace = TRUE),
  Jul = sample(100:500, 10, replace = TRUE),
  Aug = sample(100:500, 10, replace = TRUE),
  Sep = sample(100:500, 10, replace = TRUE),
  Oct = sample(100:500, 10, replace = TRUE)
)

# introduce some NAs
sales[3, "Mar"] <- NA
sales[6, "Jun"] <- NA
sales[10, "Jun"] <- NA
sales[2, "Oct"] <- NA

sales
```

## Compute average sale for Jan
```{r}
sales |> 
  summarise(mean = mean(Jan))
```

## Compute average sale for Jan for each product
```{r}
sales |> 
  group_by(prod_id) |> 
  summarise(mean = mean(Jan))
```

## Compute average, min, and max sale for Jan
```{r}
sales |> 
  summarise(
    mean = mean(Jan),
    min = min(Jan),
    max = max(Jan)
  )
```

## Compute average, min, and max sale for Jan for each product
```{r}
sales |> 
  group_by(prod_id) |> 
  summarise(
    mean = mean(Jan),
    min = min(Jan),
    max = max(Jan)
  )
```

## Compute average sale for each month

### Option 1: Call the existing mean function directly
```{r}
sales |> 
  summarise(across(-prod_id, mean))
```

Since some months has missing value, we have to instruct the mean function to remove them.

### Option 2: call the mean function indirectly in order to pass it more arguments 
Option 2a: Create a user-defined function
```{r}
calc_mean <- function(x) {
  mean(x, na.rm = TRUE)
}

sales |> 
  summarise(across(-prod_id, calc_mean))
```

Option 2b: Create anonymous function (Lambda Expression) v1
```{r}
sales |> 
  summarise(across(-prod_id, function(x) {mean(x, na.rm = TRUE)}))
```

Option 2b: Create anonymous function (Lambda Expression) v2
```{r}
sales |> 
  summarise(across(-prod_id, \(x) {mean(x, na.rm = TRUE)}))
```

Option 2b: Create anonymous function (Lambda Expression) v3 (if its body is one line)
```{r}
sales |> 
  summarise(across(-prod_id, \(x) mean(x, na.rm = TRUE)))
```

Option 2b: Create anonymous function (Lambda Expression) v4 (old)
```{r}
sales |> 
  summarise(across(-prod_id, ~ mean(.x, na.rm = TRUE)))
```


### Compute average, min, and max sale for each month
```{r}
sales |> 
  summarise(
    across(
      -prod_id,
      list(
        mean = \(x) mean(x, na.rm = TRUE),
        min  = \(x) min(x, na.rm = TRUE),
        max  = \(x) max(x, na.rm = TRUE)
      ))
  )
```

### Compute average, min, and max sale for each month for each product
```{r}
sales |> 
  group_by(prod_id) |> 
  summarise(
    across(
      everything(),
      list(
        mean = \(x) mean(x, na.rm = TRUE),
        min  = \(x) min(x, na.rm = TRUE),
        max  = \(x) max(x, na.rm = TRUE)
      ))
  )
```
