---
title: "Board Game Geek"
format: html
---

API Docs: https://boardgamegeek.com/wiki/page/BGG_XML_API2

## Goal

Get top ranked physical games

## Determine Authentication

According to [Using the XML API](https://boardgamegeek.com/using_the_xml_api), an app registration is required to use nearly all uses of the API. The app can be registered by going to <https://boardgamegeek.com/applications> and clicking the button to create an application.

## Determine Endpoint

According to the [API Docs](https://boardgamegeek.com/wiki/page/BGG_XML_API2),

-   the base URL is `https://boardgamegeek.com/`, `https://rpggeek.com/`, or `https://videogamegeek.com/`
-   the file path to search the physical games (called things) is `xmlapi2/thing`

## Query Operators

There are 11 supported parameters that can be used in the query. Let's use the following:

-   stats=1 (Returns ranking and rating stats for the item.)
-   page=1 (the page of data to see for historical info, comments, and ratings data)
-   pagesize=100 (the number of records to return in paging)

## Build Request

```{r}
bearer_token <- readLines("../../../hashcx/api-keys/boardgamegeek.bearer-token")

base_url <- "https://boardgamegeek.com"
file_path <- "xmlapi2/thing"

request <- httr2::request(base_url) |> 
  httr2::req_url_path_append(file_path) |> 
  httr2::req_url_query(
    id = I(paste0(c(1:20), collapse = ",")),
    stats = 1,
    page = 1,
    pagesize = 20
  ) |>
  httr2::req_headers(
    "Authorization" = sprintf("Bearer %s", bearer_token)
  )
request
```

## Perform Request

```{r}
response <- request |>
  httr2::req_perform()
response
```

## Inspect Response

```{r}
class(response)     # OO classification
typeof(response)    # internal data type
str(response)       # internal data structure
```

## Pull XML Docu from Response

```{r}
xml_doc <- response |> 
  httr2::resp_body_xml()
print(xml_doc, width = 50)
```

## Inspect XML Docu Structure

```{r}
xml_doc |> 
  xml2::xml_find_first("item") |>
  xml2::xml_structure()
```

## Pull Elements from XML Docu

```{r}
find_first_in_item <- function(tag) {
  xml_doc |> xml2::xml_find_all("item") |> xml2::xml_find_first(tag)
}

results <- 
  data.frame(
  name = find_first_in_item("name") |> xml2::xml_attr("value"),
  ypub = find_first_in_item("yearpublished") |> xml2::xml_attr("value"),
  minplyer = find_first_in_item("minplayers") |> xml2::xml_attr("value"),
  maxplyer = find_first_in_item("maxplayers") |> xml2::xml_attr("value"),
  time = find_first_in_item("playingtime") |> xml2::xml_attr("value"),
  avg_rate = find_first_in_item("statistics/ratings/average") |> xml2::xml_attr("value"),
  desc = find_first_in_item("description") |> xml2::xml_text()
)
results
```

## Do Some Exploration

```{r}
results |> 
  dplyr::select(-desc) |> 
  dplyr::arrange(desc(avg_rate)) |> 
  gt::gt()
```
