---
title: "Pokemon"
---

API Docs: https://pokeapi.co/docs/v2

## Goal

Get the list of creatures that inhabit the world of the Pokémon games then do basic explorations on the results.


## Determine Endpoint

According to the API Docs (from the table of **Content** --> select **Pokémon** --> select **Pokemon**), the list of creatures can be obtained by calling the resource end point https://pokeapi.co/api/v2/pokemon without a resource ID or name.


## Determine Authentication

No authentication required


## Build Request
```{r}
base_url <- "https://pokeapi.co/api/v2"
file_path <- "pokemon"
limit <- 2000

request <- httr2::request(base_url) |> 
  httr2::req_url_path_append(file_path) |> 
  httr2::req_url_query(limit = limit)
request
```

## Perform Request
```{r}
response <- request |> 
  httr2::req_perform()
response
```

### Inspect Response
```{r}
class(response)     # OO classification
typeof(response)    # internal data type
str(response)       # internal data structure
```

### Pull Results from Response
```{r}
results <- response |> 
  httr2::resp_body_json() |>
  getElement("results") |>
  dplyr::bind_rows()
results
```


## Do Some Exploration

What is the distribution of the name lengths?
```{r}
results |> 
  dplyr::select(-url) |> 
  dplyr::mutate(len = stringr::str_length(name)) |> 
  ggplot2::ggplot(ggplot2::aes(x = len)) +
  ggplot2::geom_boxplot()
```


Inspect the top 10 long names
```{r}
results |> 
  dplyr::select(-url) |> 
  dplyr::mutate(len = stringr::str_length(name)) |> 
  dplyr::slice_max(order_by = len, n = 10)
```


Inspect the bottom 10 short names
```{r}
results |> 
  dplyr::select(-url) |> 
  dplyr::mutate(len = stringr::str_length(name)) |> 
  dplyr::slice_min(order_by = len, n = 10)
```
