---
title: "U.S. Census Data"
---

API Docs: https://www.census.gov/data/developers/guidance/api-user-guide.html

## Goal

Pull data from a dataset of interest hosted by U.S. Census Data API.

## Determine Endpoint

To determine the endpoint, we need first to determine the dataset of interest.  The complete list of available datasets can be found on the [API Discovery Tool](https://api.census.gov/data.html). The dataset named "Current Population Survey: Basic Monthly" for February 2026 looks promising; let's use it.  According to the tool, the API end point for the selected dataset is https://api.census.gov/data/2026/cps/basic/feb.

## Determine Variables

The dataset contains many variables which can be found on https://api.census.gov/data/2026/cps/basic/feb/variables.html.  Let's get the following variables:

- PRUNEDUR: Labor Force-unemployment duration
- PRUNTYPE: Labor Force-unemployment reason
- STATE: FIPS STATE Code

We would like to get data only for Minnesota (STATE = 27) and Wisconsin (STATE = 55)

## Determine Authentication

The U.S. Census Data API required (free) key registration when passing the [Query Limits](https://www.census.gov/data/developers/guidance/api-user-guide.Help_&_Contact_Us.html).  The website contain instructions on how to obtain such key.


## Build Request
```{r}
us_census_data_api_key <- readLines("../../../hashcx/api-keys/us-census-data.key")

base_url <- "https://api.census.gov"
file_path <- "data/2026/cps/basic/feb"

request <- httr2::request(base_url) |> 
  httr2::req_url_path_append(file_path) |> 
  httr2::req_url_query(
    get = c("PRUNEDUR", "PRUNTYPE"),
    `for` = I("state:27,55"),
    key = us_census_data_api_key,
    .multi = "comma"
  )
request
```

## Perform Request
```{r}
response <- request |> 
  httr2::req_perform()
response
```

### Inspect Response
```{r}
class(response)     # OO classification
typeof(response)    # internal data type
str(response)       # internal data structure
```

### Pull Results
```{r}
data <- response |> 
  httr2::resp_body_json(simplifyVector = TRUE) |> 
  janitor::row_to_names(1) |> 
  dplyr::as_data_frame() |> 
  dplyr::mutate(across(c(PRUNEDUR, PRUNTYPE), as.numeric))
data
```


## Do Some Exploration

```{r}
data |> 
  dplyr::filter(PRUNEDUR != -1 | PRUNTYPE != -1) |> 
  dplyr::group_by(state) |> 
  dplyr::summarise(across(c(PRUNEDUR, PRUNTYPE), list(
    n = \(x) dplyr::n(),
    min = \(x) min(x),
    mean = \(x) mean(x),
    max = \(x) max(x)
  ))) |> 
  tidyr::pivot_longer(cols = -state) |> 
  tidyr::pivot_wider(names_from = state, values_from = value) |>
  dplyr::mutate(name = stringr::str_remove(name, ".*_")) |> 
  gt::gt(rowname_col = "name") |> 
  gt::tab_row_group(
    label = "PRUNEDUR",
    rows = 1:4) |> 
  gt::tab_row_group(
    label = "PRUNTYPE",
    rows = 5:8)
```

