---
title: "X"
---

API Docs: https://docs.x.com/overview

## Goal

Get some latest tweets


## Determine Endpoint

According to the [API Docs](https://docs.x.com/x-api/posts), the file path to search posts from last 7 days is `/2/tweets/search/recent`


## Determine Authentication

According to the [Getting Access page](https://docs.x.com/x-api/getting-started/getting-access), a developer account with app credentials is required.  As of March 24, 2026, there are four types of credentials:

- **Bearer Token**: App-only authentication for reading public data which is gest for searching posts, looking up users, reading trends.
- **Access Token & Secret**: Make requests on behalf of your own account (OAuth 1.0a) which is best for testing, personal bots, your own automation.
- **API Key & Secret**: Identify your app. Used to generate tokens and sign OAuth 1.0a requests which is best for posting, liking, following, accessing DMs.
- **Client ID & Secret**: OAuth 2.0 authentication for user-context requests.  It offers fine-grained scopes—request only the permissions you need which is best for posting, liking, following, accessing DMs.

## Query operators

[Filter operators](https://docs.x.com/x-api/posts/search/introduction#query-operators)

- `-is:retweet` Exclude retweets
- `-is:reply`  Exclude replies
- `lang:en` Posts in a English language
- `is:verified` Posts by verified users

## Build Request
```{r}
bearer_token <- readLines("../../../hashcx/api-keys/x.bearer-token")

base_url <- "https://api.x.com/"
file_path <- "2/tweets/search/recent"

request <- httr2::request(base_url) |> 
  httr2::req_url_path_append(file_path) |> 
  httr2::req_url_query(
    query = "RStats lang:en -is:retweet -is:reply",
    tweet.fields = I("created_at,public_metrics,author_id"),
    max_results = 100
  ) |> 
  httr2::req_headers(
    "Authorization" = sprintf("Bearer %s", bearer_token)
  )
request
```


## Perform Request
```{r}
# Querying the X API will cost come money.  So, we should get new data only when needed.

response_file_name <- "x-response.rds"
if (FALSE) {
  response <- request |> httr2::req_perform()
  saveRDS(response, file = response_file_name)
}
response <- readRDS(response_file_name)

response
```

### Inspect Response
```{r}
class(response)     # OO classification
typeof(response)    # internal data type
str(response)       # internal data structure
```

### Pull Results from Response
```{r}
results <- response |> 
  httr2::resp_body_json() |> 
  getElement("data") |>
  purrr::map(\(x) purrr::list_flatten(x, name_spec = "{inner}")) |> 
  dplyr::bind_rows()
results
```


## Do Some Exploration

Top re-tweeted posts
```{r}
results |> 
  dplyr::slice_max(order_by = retweet_count, n = 10) |> 
  dplyr::select(retweet_count, text) |> 
  gt::gt()
```

